### 2012-03-29 contents.tex
Overall revision.

However, mining bug repositories has its own risks. Previous research has identified problems of missing data \cite{Aranda2009} (e.g., rationale, traceability links between reported bug fixes and source code changes), inaccurate data (e.g., misclassification of bugs) \cite{Antoniol2008}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

	It should be noted that regular expressions may not be a reliable alternative to the problem of identifying verification techniques in comments. In future research, more advanced information retrieval techniques should be explored. Nevertheless, regular expressions should enable an initial study and help unveil insights about verification techniques in bug reports.

@@

	Each of the three analysis was performed on Eclipse/Platform, Eclipse/EMF, NetBeans/Platform, and NetBeans/VersionControl. The results are presented next.

@@

	In both NetBeans subprojects it is possible to infer the existence of a QA team, composed by approximately 20\% of the developers, performing at least 80\% of all verifications. In the Eclipse subprojects, there is no evidence of a dedicated QA team. Further evidence was found by looking for the substring ``QA team'' in the comments associated with the status \VERIFIED\ and \REOPENED. Comments referring to a QA team were only found in NetBeans subprojects.

@@

	By sorting through comments, we have found that many of them do not provide any clue about the verification technique used. Most often, developers just state that the bug fix was verified, sometimes informing the build used to verify the fix.

@@

	In Eclipse/Platform, comments show that the developer who fixes a bug often asks someone else to verify the fix, by asking ``please verify, [developer name]''. If the bug is reopened, then the fixer and the verifier exchange roles. This behavior illustrates a structured bug fixing/verification process.

@@

\small{This work is supported by FAPESB (grant BOL0119/2010) and CNPq/INES (grant 573964/2008-4).}

>>>>

However, mining bug repositories has its own risks. Previous research has identified problems of missing data (e.g., rationale, traceability links between reported bug fixes and source code changes) \cite{Aranda2009}, inaccurate data (e.g., misclassification of bugs) \cite{Antoniol2008}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

	It should be noted that regular expressions may not be a reliable alternative to the problem of identifying verification techniques in comments. In future research, more advanced information retrieval techniques should be explored. Nevertheless, regular expressions enable an initial study and help unveil insights about verification techniques in bug reports.

@@

	Each of the three analyses was performed on Eclipse/Platform, Eclipse/EMF, NetBeans/Platform, and NetBeans/VersionControl. The results are presented next.

@@

	In the Eclipse subprojects, there is no evidence of a dedicated QA team. In both NetBeans subprojects, on the other hand, it is possible to infer the existence of a QA team, composed by approximately 20\% of the developers, performing at least 80\% of all verifications. Further evidence was found by looking for the substring ``QA team'' in the comments associated with the status \VERIFIED\ and \REOPENED. Comments referring to a QA team were only found in NetBeans subprojects.

@@

	By reading comments, we have found that many of them mention any verification technique. Most often, developers just state that the bug fix was verified, sometimes informing the build used to verify the fix.

@@

	In Eclipse/Platform, comments show that the developer who fixes a bug often asks someone else to verify the fix, by asking ``please verify, [developer name]''. If the bug is reopened, then the fixer and the verifier exchange roles. This behavior illustrates a structured bug fixing/verification process and supports the conclusion that there is no QA team in Eclipse/Platform.

@@

%\small{
This work is supported by FAPESB under grant BOL0119/2010 and by CNPq/INES under grant 573964/2008-4.% er wer wer wer we rwe rwe rwe rwe rwe rw erw er wer wer wer wer wer wer wer wer  qwe qwe qwe qwe qwe qwe qwe qw eqwe  qwe qwe qwe qwe q qwe qwe qwe qw e
%}
